Pteropod physiological analysis

### 2018-04-02 biomark.Rmd
effects plots with confidence intervals, added observed data to surface plots

  dat <- prd_vl() %>% 
    spread_(key_col = names(.)[2], value_col = names(.)[1]) %>% 
    .[,-1] %>% 
    as.matrix

  scene <- list(
    aspectmode = 'manual', 
    aspectratio = list(x = 1, y = 1, z = 0.5), 
    xaxis = list(title = names(prd_vl()[3])),
    yaxis = list(title = names(prd_vl()[2])),
    zaxis = list(title = names(prd_vl()[1]))
    )

  p <- plot_ly(z = ~dat) %>% add_surface(colors = rev(RColorBrewer::brewer.pal(11, 'Spectral'))) %>% 
    layout(scene = scene)
  p

})
```

>>>>

  # observed data
  toplo <- md()$model
  names(toplo) <- c('z', 'x', 'y')

  # surface data
  dat <- prd_vl() %>% 
    spread_(key_col = names(.)[2], value_col = names(.)[1]) %>% 
    as.matrix
  x <- colnames(dat)[-1] %>% as.numeric
  y <- dat[, 1]
  dat <- dat[, -1]

  scene <- list(
    aspectmode = 'manual', 
    aspectratio = list(x = 1, y = 1, z = 0.6), 
    xaxis = list(title = names(prd_vl()[2])),
    yaxis = list(title = names(prd_vl()[3])),
    zaxis = list(title = names(prd_vl()[1]))
  )

  p <- plot_ly() %>% 
    add_surface(z = ~dat, x = ~x, y = ~y, colors = rev(RColorBrewer::brewer.pal(11, 'Spectral'))) %>% 
  add_markers(data = toplo, x = ~x, y = ~y, z = ~z) %>% 
    layout(scene = scene, width = 800, height = 400)
  p
})
```

### 2018-04-02 figures.Rmd
effects plots with confidence intervals, added observed data to surface plots

p1 <- ggplot() +
  geom_line(data = pl1[[1]], aes(x = Ara, y = LPX, group = pH, colour = pH), size = 1) + 
  geom_text(data = pl1[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('LPX') +
  ggtitle("(a) Synergistic effect of pH on aragonite\nsaturation")

@@

p2 <- ggplot() +
  geom_line(data = pl2[[1]], aes(x = Ara, y = LPX, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl2[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('LPX') +
  ggtitle("(b) Negative additive effect below threshold of\n temperature on aragonite saturation")

@@

p3 <- ggplot() +
  geom_line(data = pl3[[1]], aes(x = Ara, y = SOD, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl3[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('SOD') +
  ggtitle("(c) Negative additive effect of temperature on \naragonite saturation")

@@

p4 <- ggplot() +
  geom_line(data = pl4[[1]], aes(x = O2, y = abu, group = pCO2, colour = pCO2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Synergistic effect of O2 on\npCO2 stress")

@@

p5 <- ggplot() +
  geom_line(data = pl5[[1]], aes(x = Ara, y = dis, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl5[[2]], aes(x= x, y = y, label = lab), hjust = 1) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Shell dissolution') +
  scale_x_continuous(expression(Omega[Ar])) +
  ggtitle("(b) Synergistic effect of temperature on \naragonite saturation")

>>>>

p1 <- ggplot() +
  geom_ribbon(data = pl1[[1]], aes(x = Ara, ymin = LPX - se.fit, ymax = LPX + se.fit, group = pH), alpha = 0.5, fill = 'grey') +
  geom_line(data = pl1[[1]], aes(x = Ara, y = LPX, group = pH, colour = pH), size = 1) + 
  geom_text(data = pl1[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('LPX') +
  ggtitle("(a) Synergistic effect of pH on aragonite\nsaturation")

@@

p2 <- ggplot() +
    geom_ribbon(data = pl2[[1]], aes(x = Ara, ymin = LPX - se.fit, ymax = LPX + se.fit, group = Temp), alpha = 0.5, fill = 'grey') +
  geom_line(data = pl2[[1]], aes(x = Ara, y = LPX, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl2[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('LPX') +
  ggtitle("(b) Negative additive effect below threshold of\n temperature on aragonite saturation")

@@

p3 <- ggplot() +
    geom_ribbon(data = pl3[[1]], aes(x = Ara, ymin = SOD - se.fit, ymax = SOD + se.fit, group = Temp), alpha = 0.5, fill = 'grey') +
  geom_line(data = pl3[[1]], aes(x = Ara, y = SOD, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl3[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_x_continuous(expression(Omega[Ar])) +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('SOD') +
  ggtitle("(c) Negative additive effect of temperature on \naragonite saturation")

@@

p4 <- ggplot() +
  geom_ribbon(data = pl4[[1]], aes(x = O2, ymin = abu - se.fit, ymax = abu + se.fit, group = pCO2), alpha = 0.5, fill = 'grey') +
  geom_line(data = pl4[[1]], aes(x = O2, y = abu, group = pCO2, colour = pCO2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Synergistic effect of O2 on\npCO2 stress")

@@

p5 <- ggplot() +
  geom_ribbon(data = pl5[[1]], aes(x = Ara, ymin = dis - se.fit, ymax = dis + se.fit, group = Temp), alpha = 0.5, fill = 'grey') +
  geom_line(data = pl5[[1]], aes(x = Ara, y = dis, group = Temp, colour = Temp), size = 1) + 
  geom_text(data = pl5[[2]], aes(x= x, y = y, label = lab), hjust = 1) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Shell dissolution') +
  scale_x_continuous(expression(Omega[Ar])) +
  ggtitle("(b) Synergistic effect of temperature on \naragonite saturation")
